Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-04-18 paper/ms.tex
Remove torque varying with ps

In addition to $I_6$, we allowed for another free parameter - the torque from
the gas phase on the bar, $\tau_{\textrm{gas}}$. This torque is applied to the
bar in the same way as the torque from the halo is applied. The torque is given
in code units ($10^{10}\Msun \left(\kms\right)^2$). We allow this torque to
mildly vary with pattern speed according to the formula,
\begin{equation}
\tau = \tau_{\textrm{gas}} + (40 - \Omega_{\textrm{p}})\textrm{,}
\end{equation}
where $\Omega_{\textrm{p}}$ is given in $\kms/\textrm{kpc}$. We are motivated to
do this because of our result in Appendix~\ref{app:varyps} which shows that more
slowly rotating bars have higher gas infall rates and thus larger positive
torques. In the $\tau_{\textrm{gas}}=0$ case, we do not allow the gas torque to
vary with pattern speed.

>>>>

In addition to $I_6$, we allowed for another free parameter - the torque from
the gas phase on the bar, $\tau_{\textrm{gas}}$. This torque is applied to the
bar in the same way as the torque from the halo is applied. The torque is given
in code units ($10^{10}\Msun \left(\kms\right)^2$).
